Verifying Demonstrations

### 2020-03-11 paper/DB-Schnorr-nbit.tex
Adds proof for nbit ZKPK (#9)

>>>>

\subsection{\Acl*{ZK} and \acl*{PK}}\label{UWB-ZKPK}

The main difference between this protocol and the Schnorr protocol is that we 
have the prover compute responses for two different challenges, \(c_0, c_1\).
In the authentication step, the verifier chooses only one of those challenges.
However, the verifier requests all \(|q|\) bits of \(s_b\) and \(l\) bits of 
\(s_{1-b}\).

This is \iacl{PK}:
Completeness and soundness follows from the Schnorr protocol.
The knowledge extractor works exactly the same.
It does not matter that the verifier first chooses two challenges and later 
reveals which one to use and the prover sends the response bit-by-bit.

This is \emph{computational} \acl{ZK}:
The simulator chooses \[
  s_0, s_1\rgets \ZZ_q; \quad
  c_0, c_1\rgets \bin^k; \quad
  b\rgets \bin.
\]
Then it can set \[
  R_0\gets g^{s_0} A^{c_0}, \quad
  R_1\gets g^{s_1} A^{c_1}.
\]
Now the simulator must come up with those \(l\) bits.
\Cref{l-bit-advantage,DBSPtoDLP} say that distinguishing these bits from random 
is as hard as the \ac{DLP}.
So, the simulator can simply choose the \(l\) bits~\(L\rgets \bin^l\) uniformly 
at random.

The simulator outputs \(R_b, c_0, c_1, s_b, L\).

%Therefore the standard proof for Schnorr as a malicious-verifier \ac{ZKPK} 
%protocol with soundness error \(2^{-k n}\) still 
%holds~\cite[\eg][]{OnSigmaProtocols}.
%(We note that \(l\), which is also the length of the challenge bit string, must 
%be logarithmic in the security parameter, \(\lambda\), for a malicious 
%verifier.)
